%---------------------------------------------------------
  \cventry
    {Python 3, Keras} % Affiliation/role
    {SymNet} % Organization/group
    {} % Location
    {Jun 2019 - Present} % Date(s)
    {
      Created a high-level deep learning framework with a custom adaptive learning rate scheduler, novel activation functions, and built-in data pre-processing. The framework also picks reasonable default network architectures.
    }

%---------------------------------------------------------
  \cventry
    {HTML, CSS, JavaScript, Electron} % Affiliation/role
    {JournalBear} % Organization/group
    {} % Location
    {Jun. 2017 - Feb 2019} % Date(s)
    {
      Cross-platform journal application with AES-256 encryption. Downloaded 1,000 times and rated 4/5 by Softpedia.
    }

%---------------------------------------------------------
  \cventry
    {MongoDB, Node.js, Express, React} % Affiliation/role
    {Result Scraper} % Organization/group
    {} % Location
    {Mar 2018} % Date(s)
    {
      Website for scraping university examination results and displaying charts and printable reports, with caching using a database.
    }

%---------------------------------------------------------
  \cventry
    {HTML/CSS, Sass, Flexbox, React.js, React-Router v4, MySQL, Express.js, Node.js, ElasticSearch} % Affiliation/role
    {Video Sharing Website} % Organization/group
    {} % Location
    {Sep 2017 - Nov 2017} % Date(s)
    {
      Simplified implementation of a video-sharing website with subscriptions and custom searching.
    }

%---------------------------------------------------------
  \cventry
    {VB.NET, Python 3} % Affiliation/role
    {Xtreme Calculations} % Organization/group
    {} % Location
    {Apr 2013 - Oct 2017} % Date(s)
    {
      Windows math software to solve scientific and mathematical problems. Downloaded 20,000 times and rated 4/5 by Softpedia and 10/10 by Softonic.
    }

%---------------------------------------------------------
  \cventry
    {JavaScript, React.js, D3.js, Sass, Node.js, Express.js, MongoDB} % Affiliation/role
    {Web Development Projects} % Organization/group
    {} % Location
    {2017} % Date(s)
    {
      Projects include URL shortener, rogue-like dungeon crawler game, voting application, Simon game, land surface temperature heatmap, and mapping meteorite impacts across the globe.
    }