%-----------EXPERIENCE-----------------
\section{Employment}
  \resumeSubHeadingListStart
    \industryPosition
      {Amazon}{New York, NY}
      {Software Dev Engineer Intern}{May 2023 -- Aug 2023}
      {
      \resumeItemListStart
        \resumeItem{}{Implemented profile locks for Prime Video on Echo Show devices.}
        \resumeItem{Technology: }{React Native, TypeScript}
      \resumeItemListEnd
      }
  
    \researchPosition
      {North Carolina State University}{Raleigh, NC}
      {Graduate Teaching Assistant}{Aug 2022 -- Apr 2023}
      {
      \resumeItemListStart
        \resumeItem{}{TA (with 3 others) for 119 students for a graduate Automated Software Engineering class.}
        \resumeItem{}{TA (with 4 others) for 243 students for a graduate Software Engineering class.}
      \resumeItemListEnd
      }

    \researchPosition
      {North Carolina State University}{Raleigh, NC}
      {Graduate Research Assistant}{Jan. 2020 -- May 2022}
      {
      \resumeItemListStart
        \resumeItem{Better, faster deep learning for SE: }{Improved defect prediction by up to 123\% (F-1 score), code smell detection by up to 30\% (AUC)}
        \resumeItem{Semi-supervised learning: }{Achieved state-of-the-art results on static code warnings analysis using 10\% labels.}
      \resumeItemListEnd
      }

    \researchPosition
      {North Carolina State University}{Raleigh, NC}
      {Graduate Teaching Assistant}{Aug. 2019 -- Jan. 2020}
      {
      \resumeItemListStart
        \resumeItem{}{Held office hours for 54 undergraduate students and delivered lectures on C++.}
      \resumeItemListEnd
      }

    \industryPosition
      {Amazon}{Bellevue, WA}
      {Software Dev Engineer Intern}{May 2022 -- Jul 2022}
      {
      \resumeItemListStart
        \resumeItem{}{Developed a full-stack system to publish announcements in scorecards used by delivery service partners (DSPs).}
        \resumeItem{Technology: }{React/Redux, TypeScript, Redux Saga, DynamoDB, Java Spring}
      \resumeItemListEnd
      }

    \researchPosition
      {Indian Institute of Astrophysics}{Bangalore, India}
      {Research Intern}{Jul. 2018 - Mar. 2019}
      {
      \resumeItemListStart
        \resumeItem{Image denoising: }
          {Worked on image restoration of globular clusters using convolutional neural networks.}
        \resumeItem{Research: }
          {Proposed novel adaptive learning rate scheme for deep neural networks and demonstrated faster convergence by up to 100,000x.}
      \resumeItemListEnd
      }
      
  \resumeSubHeadingListEnd
