\definecolor{js}{rgb}{0.945, 0.878, 0.353}
\definecolor{py}{rgb}{0.208, 0.447, 0.647}
\definecolor{swift}{rgb}{1.0, 0.675, 0.271}
\definecolor{vb}{rgb}{0.58, 0.365, 0.718}
\definecolor{cpp}{rgb}{0.953, 0.294, 0.49}

\newif\ifshowchips
\showchipsfalse

\newcommand{\javascript}{\ifshowchips \fcolorbox{js}{js}{\bf \scriptsize JS} \fi}
\newcommand{\python}{\ifshowchips \fcolorbox{py}{py}{\bf \scriptsize \textcolor{white}{Python}} \fi}
\newcommand{\swift}{\ifshowchips \fcolorbox{swift}{swift}{\bf \scriptsize Swift} \fi}
\newcommand{\vbnet}{\ifshowchips \fcolorbox{vb}{vb}{\bf \scriptsize \textcolor{white}{VB.NET}} \fi}
\newcommand{\cpp}{\ifshowchips \fcolorbox{cpp}{cpp}{\bf \scriptsize C++} \fi}

%-----------PROJECTS-----------------
\section{Relevant Projects}
  \resumeSubHeadingListStart
  
    \ifwebdev
    \resumeSubheading
      {RateMyProgram.org \javascript}
      {Apr 2022 -- Present}
      {React, MongoDB, Sass, Azure}
      {\href{https://github.com/yrahul3910/ratemyprogram}{GitHub} :: \href{https://ratemyprogram.org/}{Website}}
      \projectDescription{Website to rate and view ratings of graduate school programs.}
    \fi
  
    \ifwebdev
    \resumeSubheading
      {Reddit Timer \javascript}
      {Apr. 2021 -- Present}
      {React, Styled Components, Sass}
      {\href{https://github.com/profydev/reddit-timer-yrahul3910}{GitHub}}
      \projectDescription{Website to help marketing teams time posts on Reddit for maximum attention.}
    \fi
  
    \ifios
    \resumeSubheading
      {SendToFuture \swift}{Apr. 2021 -- May 2021}
      {iOS, Swift}{\href{https://github.com/yrahul3910/send-to-future}{GitHub}}
      \projectDescription{iOS app to ``snooze" links for a few hours.}
    \fi
      
    \ifml
    \resumeSubheading
      {Google/Meta Data Mining \python}{Feb. 2021 -- May 2021}
      {Python, Keras}{\href{https://github.com/yrahul3910/google-takeout-data-mining}{GitHub}}
      \projectDescription{Data science project to use Google Takeout and Meta user data to suggest products to advertise to a user from Amazon best sellers using DistilGPT-2 and achieved 0.6 F-1 score.}
    \fi
      
    \ifwebdev
    \resumeSubheading
      {Threaded Discussions Website \javascript}{Feb. 2021 -- June 2021}
      {MongoDB, Node.js, React}{\href{https://github.com/yrahul3910/threaded-discussions}{GitHub}}
      \projectDescription{Companion website for video calls that allows for Reddit-style, threaded discussions.}
    \fi
  
    \ifios
    \resumeSubheading
      {NearConnect \swift}{Nov. 2020 -- Mar. 2021}
      {iOS, Swift}{\href{https://github.com/yrahul3910/socialqr}{GitHub} :: \href{https://apps.apple.com/us/app/nearconnect/id1547157546}{App Store}}
      \projectDescription{iOS app to connect with people nearby using multicast peer-to-peer connections.}
    \fi
    
    \ifml
    \resumeSubheading
      {RAISE \python}{Aug. 2020 -- Present}
      {Python, Keras}{\href{https://github.com/yrahul3910/raise}{GitHub} :: \href{https://pypi.org/project/raise-utils/}{PyPI}}
      \projectDescription{Sole developer for a PEP8/PEP257-compliant, ML Python package used by our research lab and others for replicable results. Downloaded 12k times.}
    \fi
    
    \ifml
    \resumeSubheading
      {Personalized Chatbot \python}{May 2019}
      {Python, Keras}{\href{https://github.com/yrahul3910/gpt-2}{GitHub}}
      \projectDescription{Fine-tuned a GPT-2 345M model on 730k messages from Telegram logs to create a personalized chatbot.}
    \fi
    
    \ifml
    \resumeSubheading
      {Intelligent Tutoring System \python}{Sep. 2018 -- May 2019}
      {Python}{\href{https://github.com/yrahul3910/student-modeling-project}{GitHub}}
      \projectDescription{Implemented an Intelligent Tutoring System backend using Bayesian Knowledge Tracing and a novel question selection algorithm.}
    \fi
      
    \ifml
    \resumeSubheading
      {Human Activity Data Project \python}{Oct. 2018 -- Nov. 2018}
      {Python, Keras}{\href{https://github.com/yrahul3910/ActivityDataProject}{GitHub}}
      \projectDescription{Collected personal activity data for 9 months, grouped tasks into 21 categories. Analyzed most productive hours of the day and built a 2-layer predictive LSTM model, achieving 42\% top-5 accuracy.}
    \fi
    
    \ifdesktop
    \resumeSubheading
      {JournalBear \python}{Jun. 2017 -- Feb. 2019}
      {JavaScript, Electron}{\href{https://github.com/yrahul3910/journal}{GitHub}  :: \href{https://www.softpedia.com/get/Office-tools/Diary-Organizers-Calendar/JournalBear.shtml}{Softpedia}}
      \projectDescription{Cross-platform journal application with AES-256 encryption. Rated 4/5 by Softpedia.}
    \fi
    
    \ifwebdev
    \resumeSubheading
      {Results Scraper \javascript}{Mar. 2018 -- Aug. 2018}
      {MongoDB, Express, React, Node.js}{\href{https://github.com/yrahul3910/results-scraper-node}{GitHub}}
      \projectDescription{Website for scraping university examination results and displaying charts and printable reports, with caching using a database.}
    \fi
      
    \ifwebdev
    \resumeSubheading
      {Video Sharing Website \javascript}{Oct. 2017 -- Dec. 2017}
      {MySQL, Express, React, Node.js, Sass, Elasticsearch}{\href{https://github.com/yrahul3910/video-sharing-site}{GitHub}}
      \projectDescription{Simplified implementation of a video-sharing website with subscriptions and custom searching.}
    \fi
      
    \ifdesktop
    \resumeSubheading
      {Xtreme Calculations \vbnet}{Apr. 2013 -- Oct. 2017}
      {VB.NET, Python}{\href{https://www.softpedia.com/get/Science-CAD/Xtreme-Calculations.shtml}{Softpedia}}
      \projectDescription{Windows math software to solve scientific and mathematical problems, with over 30,000 downloads over multiple sites.}
    \fi
      
    \ifdesktop
    \resumeSubheading
      {Video Indexer \cpp}{Jun. 2017 -- Sep. 2017}
      {C++, Qt, CMUSphinx}{\href{https://github.com/yrahul3910/video-indexer}{GitHub}}
      \projectDescription{Cross-platform desktop application to detect the time(s) a given keyword was spoken in a given video.}
    \fi
      
    \ifwebdev
    \resumeSubheading
      {Web development projects \javascript}{Jan. 2017 -- Nov. 2017}
      {MongoDB, Express, React, Node.js, D3, Sass}{\href{https://github.com/yrahul3910/video-indexer}{GitHub}}
      \projectDescription{Projects include URL shortener, rogue-like dungeon crawler game, voting application, Simon game, land surface temperature heatmap, and mapping meteorite impacts across the globe.}
    \fi
  \resumeSubHeadingListEnd